\subsection{Review of Nick Boe Elsborg; Vision and Hearing as Perceptual Systems - Similarities and Differences}


Good \textbf{introduction} and elaboration of what the essay will cover.\\
The \textbf{theory section} mentions "events", this can be unclear for the reader, a potential edit could just be to write shortly what the event is in regards to. e.g; "events, e.g. a person walking or rock colliding with a surface".\medskip \\
In \textbf{section 2.2}, paragraph one, "aid in its identification and/or categorization", this can be unclear to the reader in regards to what the author meant. What is meant by identification and categorization? A solution could be to shortly cover what the words are in regards to.\\The section is general is very nicely ordered, explained and concise. Good refs and statements.\medskip \\
\textbf{Section 2.4}, concise explanations of what frequency, amplitude and waveform is, might be a bit squished or rushed explanation but the authors point can be understood.\\First sentence in \textbf{2.4.1} seems out of place, either could be deleted or rephrased, Paragraph 2 is missing a ref for the statement but else it's a good explanation and also good comparison between how the two ears can relate more or less to how the two eyes function in terms of depth. Paragraph 4 could also use a reference or two for the statements on doppler effect.\\\textbf{Section 2.4.2}, even though the abstract words have footnotes, it still needs references for the statements made. Else the section is quite nice, fact heavy but the author clearly tried to keep it simple whilst also giving off the understanding properly.\medskip \\
In \textbf{section 2.5}, first sentence is very odd and could potentially seem out of place for the reader, a potential edit could be; "[...] which is then converted to X representation, that COMPARES it with the brains memory".\\It's although very clear the author has given both topics thought when comparing sounds to visual, this is in regards to the EST comparsion when listening to footsteps instead of seeing it visually.\medskip \\
In \textbf{section 3, the discussion}, the author provides good claims of how changing related features of a certain object in regards to its sorroundings in a digital scene, could have drastic effects on how the person will perceive the object compared to how their usual expectations were for said object.\\It's also very nice that the Author shows thought in relation to his semester project, that inhibiting the visuals of his prototype could increase the focus on the auditory aspects of it when a user uses it.\\Overall the discussion is good, but paragraph 3 especially seems a bit out of place and could potentially be read as more of a fact than a discussion. Either explain the others in more detail or drop paragraph 3.\medskip \\
\underline{Overall}\\
Very few gramatical mistakes, and none were sufficient enough to make the user unable to understand what was being told by the author, the refs are very nicely done and the sources are credible correct where needed, especially with pagenumbering and the factual content is exhaustive and accurate. The essay can seem pressured in some sections due to word limitations, as the author was close to exceed those limits in small occurances in the essay. The reader can easily understand what is being relayed through the topics.\\
In terms of learning goals, all are covered which relates to the semester project of the author, you could discuss whether or not top-down and bottom-up information, masking or how the auditory system specifically detects sounds are really needed to cover the semester project, but that I would argue is not needed.\\
Also plus points for writing the essay in \LaTeX


%Is the factual content correct?
%Is the report of adequate length? (2000-2500 words excluding references)  YES
%Does the author demonstrate knowledge of the topics corresponding to the learning goals? YES
%Is the content organized and presented in such a way that a reader can follow the reasoning? YES
%What sources are used and are they cited and referenced properly? YES
%////////////////////////////////

