\subsection{Review of Mathias Friis Jensens; Human depth perception and the Kinect depth sensor}

Section \textbf{"Vision"}; explanation of how vision occours is fine, although the end of paragraph 1 is missing a reference to the statement made in regards to sensors. Also the author makes it sound like the light is captured by pixels which are the RGB-values. This is incorrect and a potential edit could be; "The light is captured by the cells in the sensor, which are then converted to a digital image by a converter."\\Paragraph 2 is also missing a reference, in regards to how we perceive depth in the world. Good transition from one section to the next, but very extensive and not neccesarily needed, e.g. a potential edit could be to shorten the paragraph to "There are many similarities between a camera and an eye, the depth perception is although very unique in this situation and will therefore be compared to other system in the next section.".\\

Section \textbf{"Depth perception through eye and sensor"}; It is hard to check the factual statement made about "Convergence", since it is missing a reference to the material explained. Also, as explained in the course book; the angle between the eyes increases as the objects distance from the eye decreases. The explanation from the author could potentially confuse the reader; and edit could be "the angle between the eyes will get bigger, as the object moves closer to the eyes".\\

Section \textbf{"Binocular depth cues"}; The very first statement can potentially be confusing or misleading for the reader, as it seems the author claims that the only functionaility needed in the eye for a retinal image, is the lens which is incorrect. A potential fix could just be to delete this statement made whilst modifying the next sentence to fit the elaboration of the follow-up.\\

Section \textbf{"Stereograms"}; This section does cover the explanation of anaglyphs, the factual content is understandable for the reader but is weighed down heavily because of the missing credibility which would have been provided through a reference or citation.\\

\underline{Overall}\\
A lot of statements made in the essay are not properly referenced or completely missing the references. Examples can be seen in the Vision and Depth perception through eye and sensor sections. The author makes multiple factual statements which are never referenced or the whole section only has one reference where the author is explaining multiple things at a time.\\Some factual statements that are made in the essay wary or is unclear in regards to it validity. The author occasionally uses specific terms which are never explained in enough detail to make sense of it, the reader can potentially delve into a very confusing statement because of the lacking explanations.\\ The discussion is fine and compares the advantages and disadvantages of the topics in relation to the semester project. Although most of the elements stated are already covered throughout the rest of the essay and could arguably be redundant.\\The author clearly did research most of the topics he described, but the lacking citations and references made the validity of the statements fallible.\\Sidenote; very odd way of referencing the figures presented in the essay, else the sources, where given, are correct.
% Over 2k
%Is the factual content correct?
%Is the report of adequate length? (2000-2500 words excluding references)  YES
%Does the author demonstrate knowledge of the topics corresponding to the learning goals? YES
%Is the content organized and presented in such a way that a reader can follow the reasoning? YES
%What sources are used and are they cited and referenced properly? YES
%////////////////////////////////
