\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Meaning in Movies 1 - SM}
\author{Jannick Drews}
\date{\today}

\usepackage{natbib}
\usepackage{graphicx}

\setlength\parindent{0pt}

\begin{document}

\maketitle
\newpage
%You should analyze a movie of your own choosing, according to the taxonomy of meaning introduced during the first minimodule with Rolf Nordahl.

%For more information about the four levels and an example of an analysis please refer to Rolf’s slides from the first lecture and the document "Making Meaning" which can be found as part of the mandatory readings pertaining to this lecture. Also, last year our TAs prepared a nice document describing the taxonomy (here) and we have uploaded two examples of how previous students have answered the assignment (here and here).

%Note that you cannot expect the reader to be familiar with the movie. The assignment is to be written individually and uploaded via Moodle. If you have questions about the assignment please contact Rolf Nordahl (rn@create.aau.dk).


\section*{The Big Lebowski}
\label{sec:title}
This assignment will be based on the movie, "The Big Lebowski".
\section*{Referential Meaning}
% Referential meaning. During the Depression, a tornado takes a girl from her family's Kansas farm to the mythical land of Oz. After a series of adventures, she returns home.
A man is out to get repaid for his rug, which has been ruined by villains, this results in the main character finding out that he is not the only guy named Lebowski. The other Lebowski has had his wife kidnapped allegedly where the consequences are spilled onto the main character because of the similar names. He is continously annoyed at everyone trying to push problems and agendas, whereas he just want to have his rug back, bowl like always and relax with a white russian drink.

\section*{Explicit Meaning}
% Explicit meaning. A girl dreams of leaving home to escape her troubles. Only after she leaves does she realize how much she loves her family and friends. Nothing she finds elsewhere can replace them.
A man who just wants to bowl and have a normal life, is forced to partake in a kidnapping and is subjected to harrassment because of another mans problems. This eventually leads to his friend being out of his element and eventual death, and nothing really changes.


\section*{Implicit Meaning}
% Implicit meaning. An adolescent who must soon face the adult world yearns for a return to the simplicity of childhood, but she eventually accepts the demands of growing up.
The main character ends up being introduced to multiple different other characters, this is a result of the main character trying to reaquire his rug, which he must come to terms with is never going to happen. Him just wanting to bowl and continue the old, never changing subject of his friend having sacrificed so much in vietnam as life is just the same cycle over and over again, except this time, the cycle is broken, if only for a brief period.


\section*{Symptomatic Meaning}
% Symptomatic meaning. In a society in which human worth is measured by money, the home and the family may seem to be the last refuge of human values. This belief is especially strong in times of economic crisis, such as that in the United States in the 1930s.
% Reflect on how people want to be left alone, or how most movies always push action on the actor, the unconvetional main character in movies
This is a controversial movie, where action and people are usually introduced or even pushed on the main character as someone we expected to finally show up, either a villain or a hero. In this case, these characters are very unexpected but they themselves want to be the alleged "assistant" to the main character. The controversy being the main character this time around is just a "dude" who wants to bowl and drink beverages.
\end{document}
